On the presentation of orthogonal groups over polynomial rings

### 2019-01-13 dl-paper.tex
Added Lemma

\theoremstyle{definition}
\newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
\newtheorem{rem}[lemma]{Remark}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\colim}{colim}
\newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
\newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
\newcommand{\rA}{\mathsf{A}}
\newcommand{\rB}{\mathsf{B}}
\newcommand{\rC}{\mathsf{C}}
\newcommand{\rD}{\mathsf{D}}
\newcommand{\rE}{\mathsf{E}}
\newcommand{\rF}{\mathsf{F}}
\newcommand{\rG}{\mathsf{G}}

@@

\subsection{Isogenous forms of the orthogonal group}
\subsection{Grothendieck--Witt groups}
\section{Proof of the main result}
\subsection{Overview of the proof}
\subsection{First injectivity theorem}
\subsection{Second injectivity theorem}

>>>>

\theoremstyle{definition}
\newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
\newtheorem{rem}[lemma]{Remark}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\GW}{GW}
\DeclareMathOperator{\colim}{colim}
\newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
\newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
\newcommand{\rA}{\mathsf{A}}
\newcommand{\rB}{\mathsf{B}}
\newcommand{\rC}{\mathsf{C}}
\newcommand{\rD}{\mathsf{D}}
\newcommand{\rE}{\mathsf{E}}
\newcommand{\rF}{\mathsf{F}}
\newcommand{\rG}{\mathsf{G}}

@@

\subsection{Isogenous forms of the orthogonal group}
\subsection{Grothendieck--Witt groups}
\section{Proof of the main result}
\subsection{Overview of the proof}
\subsection{First injectivity theorem}
For a commutative ring $A$ with an ideal $M$ we denote by $B = B_{A, M}$ the subring $A[X^{-1}] + M[X]$ of the ring $R = A[X, X^{-1}]$.
It is clear that $I := M[X, X^{-1}]$ can be considered as an ideal of both $B$ and $R$.
\begin{lemma}\label{lem:lemma32} Let $\Phi$ be a simply-laced root system of rank $\geq 3$.
Consider the following commutative square of canonical maps.
\[ \xymatrix{
    \St(\Phi, B, I) \ar[r] \ar[d] & \St(\Phi, B) \ar[d] \\
    \St(\Phi, R, I) \ar[r] \ar@{-->}[ur]_\mu & \St(\Phi, R)
   } \]
Then there exists an arrow $\mu$ which makes the diagram commute.   
\end{lemma} 
\begin{proof}
 Notice that $R$ is isomorphic to the principal localisation of $B$ at $X$
  and that $I$ is uniquely $X$-divisible in the sense of~\cite[\S~4]{LS17}.
 Thus, in the special case $\Phi = \rA_3$ the assertion of the lemma follows from~\cite[Theorem~3]{LS17}.

 Now the general case can be obtained as a corollary of amalgamation theorem~\cite[Theorem~9]{S15}
  (cf.~\cite[\S~4]{LS17} for more details).
 %TODO: Also give reference on a similar result of Lavrenov
 %TODO: Rethink the proof of amalgamation theorem...
\end{proof}

\begin{lemma}
 For a field $F$ and $\ell \geq 5$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
\end{lemma}
\begin{proof}
 We have defined $\K_3(\rD_\ell, R)$ as 
\end{proof}

\subsection{Second injectivity theorem}
